\textsc{\wobble: a data-driven method for precision radial velocities}

### 2018-12-18 paper/paper.tex

\begin{figure}
\centering
\includegraphics[width=5in]{hd189_rm}
\caption{\RVs measured by \wobble for a single night of observations of the Hot Jupiter host HD 189733. The \RM is clearly seen as the planet transits the star. \todo{[blah blah starry blah]}}
\label{fig:hd189_rm}
\end{figure}

@@

The resulting \RV signal retrieved by \wobble is shown in Figure \ref{fig:hd189_rm}. 
We fit the signal using \starry \citep{Luger2018}. \todo{(RODRIGO: fill in a bit about methods)} 
\todo{(comparison of retrieved parameters to previous work here)}

>>>>

\begin{figure}
\centering
\includegraphics[width=5in]{hd189_rm}
\caption{\RVs measured by \wobble for a single night of observations of the Hot 
         Jupiter host HD 189733. The \RM is clearly seen as the planet transits 
         the star. The top panel shows the data (black points), the maximum
         likelihood fit using \starry (black curve), and 500 posterior samples
         (orange lines). The bottom panel shows the residuals of the maximum
         likelihood model fit.}
\label{fig:hd189_rm}
\end{figure}

@@

The resulting \RV signal retrieved by \wobble is shown in Figure \ref{fig:hd189_rm}. 
We fit the signal using \starry \citep{Luger2018}, which computes analytic occultation
light curves for bodies whose surfaces can be decomposed into sums
of spherical harmonics. Since the radial component of the velocity field of a 
differentially rotating star can be expressed in terms of polynomials in 
$x = \sin\theta\cos\phi$, $y = \sin\theta\sin\phi$, and $z=\cos\theta$, where
$\theta$ is the polar angle and $\phi$ is the azimuthal angle \citep[c.f. Equation 91 in][]{Short2018},
this velocity field may be expressed exactly in terms of spherical harmonics
\citep{LugerBedell2019}.
We therefore use \starry to fit for the equatorial rotational velocity, the inclination,
the obliquity, and the shear due to differential rotation of the star, closely
following the analysis performed in \citep{Cegla2016}.
We infer a projected stellar obliquity $\lambda = -0.43 \pm 0.34^\circ$, in close agreement
with the value reported in \citet{Cegla2016}. Our inferred values for the other parameters
are broadly consistent with the results in \citet{Cegla2016}, except with significantly
higher uncertainty due to the fact that we are unable to constrain the stellar inclination
due to the $v\sin i$ degeneracy. We attribute the narrower posteriors in \citet{Cegla2016}
as a difference in the choice of prior.
\footnote{See \href{https://github.com/megbedell/wobble/tree/master/scripts/DifferentialRotationWithSphericalHarmonics.ipynb}{this interactive notebook} 
          for a derivation of the spherical harmonic decomposition of the stellar velocity field. 
          The notebook used to perform our analysis and produce Figure~\ref{fig:hd189_rm} can be found 
          \href{https://github.com/megbedell/wobble/tree/master/scripts/HD189733bWithStarry.ipynb}{here}.}
